Cover Letter

### 2023-10-23 manuscript.qmd
Update

There was no clear evidence of any treatment effect of corticosteroids on substantive clinical outcomes. The effect of corticosteroids, compared with placebo or no treatment, is uncertain for maternal death, acute pulmonary edema, dialysis, and perinatal death. Corticosteroids, compared with placebo or no treatment, have little or no difference in platelet transfusion but may result in a slight reduction in acute renal failure.

@@

Our strategy aimed to study the effectiveness of corticosteroids for HELLP syndrome regarding critical maternal and perinatal outcomes rather than surrogate outcomes. While surrogate outcome measures, such as laboratory results, may provide insights into how a treatment might work, yet they do not necessarily reflect clinical benefits relevant to decision making. Moreover, some interventions that reduce the risk for a surrogate outcome may have no or harmful effects on clinically relevant outcomes, and other interventions having no effect on surrogate measures may improve clinical outcomes @Bucher2015; @cochrane2023ch3. As such, and despite their potential appeal, superiority on a surrogate end point, for example the change in platelet count and liver enzymes, may not reflect actual benefits that corticosteroids have on critical outcomes of women with HELLP syndrome. Furthermore, surrogate end points are potentially misleading and should be avoided, or at least interpreted with caution, as decision makers are required to extrapolate the findings to estimate true patient benefits, resulting in uncertainty about the effect of corticosteroids in HELLP syndrome. Published synthesized evidence @mao2015 that included surrogate outcomes without downgrading the certainty of evidence for indirectness would definitely provide misleading implications for practice. It may not be justifiable or acceptable to use surrogate outcomes for a review when validated or evaluated true endpoints are available @tufanaru2016.

>>>>

There was no clear evidence of a treatment effect of corticosteroids on substantive clinical outcomes. The effect of corticosteroids, compared with placebo or no treatment, is uncertain for maternal death, acute pulmonary edema, dialysis, and perinatal death. Corticosteroids, compared with placebo or no treatment, have little or no difference in platelet transfusion but may result in a slight reduction in acute renal failure.

@@

Our strategy aimed to study the effectiveness of corticosteroids for HELLP syndrome regarding critical maternal and perinatal outcomes rather than surrogate outcomes. While surrogate outcome measures, such as laboratory results, may provide insights into how a treatment might work, yet they do not necessarily reflect clinical benefits relevant to decision making. Moreover, some interventions that reduce the risk for a surrogate outcome may have no or harmful effects on clinically relevant outcomes, and other interventions having no effect on surrogate measures may improve clinical outcomes @Bucher2015; @cochrane2023ch3. As such, and despite their potential appeal, superiority on a surrogate end point, for example the change in platelet count and liver enzymes, may not reflect actual benefits that corticosteroids have on critical outcomes of women with HELLP syndrome. Furthermore, surrogate end points are potentially misleading and should be avoided, or at least interpreted with caution, as decision makers are required to extrapolate the findings to estimate true patient benefits, resulting in uncertainty about the effect of corticosteroids in HELLP syndrome. Published synthesized evidence @mao2015 that included surrogate outcomes without downgrading the certainty of evidence for indirectness would provide misleading implications for practice. It may not be justifiable or acceptable to use surrogate outcomes for a review when validated or evaluated true endpoints are available @tufanaru2016.
